CIVILITY: Cloud based Interactive Visualization of Tractography Brain Connectome

### 2016-07-11 doc/spiePaper/article.tex
DOC : import images

%\begin{figure}
%\centering 
%\includegraphics[width=15cm]{average_1y.png}
%\caption[Average brain connectome at 2 year old]{Average brain connectome at 1 year old}
%\label{fig:AverageBrainConnectome1YearOld}
%\end{figure}

\begin{figure}
\centering 
\includegraphics[width=15cm]{average_2y.png}
\caption[Average brain connectome at 2 year old]{Average brain connectome at 2 year old}
\label{fig:AverageBrainConnectome2YearOld}
\end{figure}

%\begin{figure}
%\centering 
%\includegraphics[width=15cm]{average_brainTemplate_1y.png}
%\caption[Average brain connectome at 2 year old]{Average brain connectome at 2 year old}
%\label{fig:AverageBrainConnectome2YearOld}
%\end{figure}

\begin{figure}
\centering 
\includegraphics[width=15cm]{average_brainTemplate_2y.png}
\caption[Average brain connectome at 2 year old]{Average brain connectome at 2 year old}
\label{fig:AverageBrainConnectome2YearOld}
\end{figure}

@@

%\begin{figure}
%\centering 
%\includegraphics[width=15cm]{variability_1y.png}
%\caption[Variability of brain connectome at 2 year old]{Average brain connectome at 1 year old}
%\label{fig:VariabilityBrainConnectome1YearOld}
%\end{figure}

\begin{figure}
\centering 
\includegraphics[width=15cm]{variability_2y.png}
\caption[Variability brain connectome at 2 year old]{Average brain connectome at 2 year old}
\label{fig:VariabilityBrainConnectome2YearOld}
\end{figure}

>>>>

\begin{figure}
\centering 
\subfigure[]{\includegraphics[width=8cm]{average_1y.png}}
\subfigure[]{\includegraphics[width=8cm]{average_2y.png}}
\caption[Average brain connectome at 1 (a) and 2 (b) year old]{Average brain connectome at 1 and 2 year old}
\label{fig:AverageBrainConnectome}
\end{figure}

\begin{figure}
\centering 
\subfigure[]{\includegraphics[width=15cm]{average_brainTemplate_1y.png}}
\subfigure[]{\includegraphics[width=15cm]{average_brainTemplate_2y.png}}
\caption[Average brain connectome at 1 and 2 year old]{Average brain connectome at 1 and 2 year old}
\label{fig:AverageBrainConnectomeBrainTemplate}
\end{figure}

@@

\begin{figure}
\centering 
\subfigure[]{\includegraphics[width=15cm]{variance_1y.png}}
\subfigure[]{\includegraphics[width=15cm]{variance_2y.png}}
\caption[Variability of brain connectome at 1 and 2 year old]{Average brain connectome at 1 and 2 year old}
\label{fig:VariabilityBrainConnectome1YearOld}
\end{figure}
